\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}

\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\centering
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]


\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}



\begin{center}
    {\LARGE Daniel Gabitov} \\ \vspace{2pt}
    \begin{multicols}{2}
    \begin{flushleft}
    Saint-Petersburg, Russia\\ 
    GitHub: \href{{https://github.com/DanielGabitov}}{\textcolor{blue}{DanielGabitov}}\\
    \end{flushleft}
    
    \begin{flushright}
    Email:  work.gabitov@gmail.com \\
    Mobile No.: 89277866211\\
    \end{flushright}
    \end{multicols}
\end{center}


%-----------EDUCATION-----------
\vspace{-2pt}
\section{Education}
  \resumeSubHeadingListStart
      \resumeSubheading
      {\textbf{Higher School of Economics}}{Russia, SPb}
      {Currently pursuing bachelors degree in applied mathematics and informatics.}{Aug. 2019 -- June. 2023}
    
  \resumeSubHeadingListEnd
  
    \resumeSubHeadingListStart
      \resumeSubheading
      {\textbf{RELEVANT COURSEWORK:}}
            {}\textbf{:}\\
\textbf{Programming courses}{: algorithms and data structures, Java, C++, UNIX, functional programming (Haskell) }\\
\textbf{Math courses}{: calculus, discrete mathematics, algebra, probability theory, formal languages}\\    
  \resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
 
    \resumeSubheading
      {2D Game}{}
      {3 participants}{March 2020 - June 2020}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
    {A platformer in which the player's goal is to paint the largest amount of blocks his specific color in a limited time.} \\
     \textbf{Tools}{: C++, QT, GIT.} \\
     \textbf{My work}{: Game logic, level-loading, game engine.}\\
     \textbf{GitHub}{: \href{{https://github.com/DanielGabitov/ProjectFivaproljo}}{\textcolor{blue}{ProjectFivaproljo}.}}
    }}
 \end{itemize}
 
  \resumeSubheading
      {Huffman Archiver}{}
      {Developed an archiver based on the Huffman algorithm that can compress and decompress both binary and text
files.}{June 2020}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Tools}{: C++.} \\
     \textbf{GitHub}{: \href{{https://github.com/DanielGabitov/HSE-C-/tree/master/hw_03}}{\textcolor{blue}{HuffmanArchiver}.}}
    }}
    
 \end{itemize}
 
 \resumeSubheading
      {Mobile app (in progress)}{}
      {3 participants}{March 2021 - Now}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
    {Android app to organize and search offline events.} \\
     \textbf{Tools}{: Java, Spring, PostgreSQL, Docker, FlyWay.} \\
     \textbf{My work}{: Backend.}\\
     \textbf{GitHub}{: \href{{https://github.com/DanielGabitov/namelessProject}}{\textcolor{blue}{NamelessProject}.}}
    }}
    
 \end{itemize}
  \resumeSubHeadingListEnd
  
  


%-----------Technical Skills-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Languages}{: C++, Java, Bash, Haskell} \\
     \textbf{Tools}{: Git, Docker, Spring, PostgreSQL, QT}\\
    }}
 \end{itemize}

%-----------Languages-----------
\section{Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{}{Russian (Native)} \\
     \textbf{}{English  (Upper-Intermediate)}\\
    }}
 \end{itemize}

\end{document}